The Lipid Interactome Repository

### 2025-03-11 index.qmd
cleaning up homepage for preview

**This repository is still under construction, please forgive us for incomplete sections as we build features!**

The goal of this site is to increase the accessibility of proteomics data utilizing multi-functionalized lipid analogs/probes to identify the lipid::protein interactions of biologically active lipids.

>>>>

<!-- **This repository is still under construction, please forgive us for incomplete sections as we build features!** -->

The goal of this site is to increase the accessibility of proteomics data utilizing multi-functionalized lipid analogs/probes to identify the lipid:protein interactions of biologically active lipids.
